Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-10-22 PaperMagneticProfiles_JBSMSE.tex
Include revised manuscript from JRB.

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{xcolor}
\usepackage{nomencl}
\usepackage{hyperref}

@@

\title{Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators}

\author{
Fábio P. Fortkamp \and
Gusttav B. Lang \and
Jaime A. Lozano \and
Jader R. Barbosa Jr.
}

\institute{
Fábio P. Fortkamp \\
\email{fabio@polo.ufsc.br} \\
Gusttav B. Lang \and
Jaime A. Lozano \and
Jader R. Barbosa Jr.
\at
POLO --- Research Laboratories for Emerging Technologies in Cooling and Thermophysics, Department of Mechanical Engineering, Federal University of Santa Catarina, Florianópolis, SC, 88040-900, Brazil}

@@

\begin{abstract}
Magnetic cooling is an alternative to vapor compression with no use of hazarduous gases. The refrigerant is a solid material which reacts to oscillations in magnetic field with changes in temperature. In active magnetic regenerators, this magnetocaloric material and its effect are coupled with an oscillating fluid flow to yield a thermodynamic cooling cycle between cold and hot source temperatures. The literature is abundant with studies on the influence of the fluid flow waveform on magnetic refrigeration devices, but the influence of the magnetic field waveform is less investigated. In this work, we simulate a previously developed active magnetic regenerator numerical model with different mathematically-defined waveforms, and determine which operating parameters yield the highest values for cooling capacity and coefficient of performance. Results show that the highests performance levels are achieved when the magnetic field is kept constant for the same duration of the fluid flow through the magnetized material, and that the transition times between high and low levels of the magnetic field should be as fast as possible.

\keywords{ magnetic refrigeration \and active magnetic regenerator \and numerical modeling \and magnetocaloric effect}
\end{abstract}

@@

Mechanical vapor compression has been the dominant cooling technology for the past century \cite{bib:nik} but, despite its dominance, it still faces an increasing number of challenges related to the its environmental footprint. In particular, the phase-out of refrigerants \textcolor{black}{with} ozone depleting \textcolor{black}{and global warming potentials has} introduced the use of flammable substances, with their own set of risks for consumer applications \cite{bib:iir-flammable} and technological challenges \cite{bib:lionte18-adapt}.

Magnetic refrigeration (MR) is an advanced cooling technology with no use of hazarduous gases, where a \emph{magnetocaloric material} (MCM) \textcolor{black}{is subjected to a cyclical change of the applied} magnetic field, and its temperature \textcolor{black}{changes as a result} of the \emph{magnetocaloric effect} (MCE). The magnitude of the MCE  \textcolor{black}{depends} on  material parameters, magnetic field variation and temperature, and its maximal at the Curie temperature of the material. For a thorough introduction to the magnetocaloric effect and magnetocaloric materials, the reader is referred to \cite{bib:smith-magneto}.

@@

For operating conditions typical of a low-temperature span magnetic refrigerator, the MCE is typically \textcolor{black}{on} the order of \num{2}-\SI{5}{\kelvin}. \textcolor{black}{T}o amplify this \textcolor{black}{temperature change}, heat regeneration is usually employed \cite{bib:kitanovski}. Active magnetic regenerators (AMR) are thermal devices where the magnetocaloric material constitutes a solid matrix through which flows an aqueous heat transfer fluid, and which is cyclically magnetized and demagnetized to activate the magnetocaloric effect.  \textcolor{black}{Such a regenerator is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously} to build up a temperature profile \textcolor{black}{along its length}. These layers can be made of the same material, yielding an homogeneous regenerator; however, given the  dependence  of the MCE with temperature, it is an interesting strategy to build \emph{multilayer} regenerators, where each layer is composed of a different material \textcolor{black}{that} will work around its \textcolor{black}{own} Curie temperature, maximizing the magnetocaloric effect of each portion.

@@

Magnetic refrigerators can operate according to different thermodynamic cycles, but the stages are roughly as follows. The magnetic circuit magnetizes the MCM, increasing its temperature due to the MCE. During the so-called \emph{cold blow}, cold fluid from the cold source flows through the warm bed and absorbs its energy, releasing it to the external heat exchanger. On the return of the fluid, the solid is demagnetized and cooled down, and in the \emph{hot blow} the fluid relases energy to the bed, decreasing its temperature so it can absorb the thermal load at the cold source. The cycle then repeats; different cycles can be configured by different durations and synchronization steps between these two \emph{characteristic waveforms}:

\begin{enumerate}
\item The \emph{magnetic profile}, which describes the oscillating magnetic field over one regenerator;
\item The \emph{fluid flow profile}, which describes the time-variation of flow rate through one bed.
\end{enumerate}

Fluid flow profiles are more easily investigated with experimental methods, since they can be altered with modifications in the fluid flow system. In particular, the \emph{duration} of blows have been extensively investigated \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}, and the literature shows that the cooling capacity of magnetic refrigerators can be increased by focusing fluid flows during periods where the magnetic field is at its extrema values.

In this work, we focus on magnetic profiles, which are less studied in the literature.
These waveforms are usually investigated in terms of their synchronization with the fluid flow profile \cite{TUSEK20111507,bib:bjoerk11_amr}. This paper uses the AMR model developed by \cite{bib:trevizoli16_perfor_model}, and the same authors had studied magnetic profiles waveforms in an earlier work \cite{bib:asme-mce}. However, their amplitudes was not varied, nor were they investigated with different geometries.

The present work combines the gaps from the above cited papers in investigating the performance of a magnetic refrigerator under different magnetic profile waveforms. These waveforms are mathematically modeled, and the cooling capacity and coefficient of performance are calculated based on the profiles parameters, while also investigated how the AMR geometry affect the performance in combinations with the magnetic profile. The fluid flow profile is assumed fixed in shape, although its parameters are also varied. To emulate constraints on an operating point of actual magnetic refrigeration devices, the temperature span is set fixed, and hence few comments are made on second-law efficiency.

@@

As previuosly explained, we perform numerical simulations of a previously developed AMR model, varying the profile-specific and geometric parameters. We also couple a model for calculating  the power comsumption of a proposed fluid management system, a topic understudied in the literature. The output of this integrated model are cooling capacity, power contributions and the coefficient of performance (COP).

@@

Simulations were performed using a one-dimensional AMR mathematical model, implemented using the Finite Volumes Method \cite{bib:trevizoli16_perfor_model}. Here we will show a summarized version focusing on the governing equations. This model solves momentum and energy balance equations for the solid and fluid phases, represented by indices `s' and `f', respectively. The model geometry is depicted in \autoref{fig:amrmodel}, and assumes regenerators composed of monodisperse packed spheres with porosity $\varepsilon$.

@@

The momentum equation for the fluid domain is:

@@

Initial and boundary conditions, solution methods, convergence analyses, and closure relations for the porous media terms are described in \cite{bib:trevizoli16_perfor_model}. This AMR model solves the above equations for one regenerator operating between given sources temperatures (assuming ideal heat exchangers in contact with the thermal reservoirs), during one full cycle (hot and cold blows and  magnetization and demagnetization periods), given specified operating conditions (to be discussed later).

The casing heat transfer term $\rate{q}\ped{csg}$ in \autoref{eq:78} is calculated solving the heat conduction in the regenerators casing \cite{bib:trevizoli16_perfor_model}, and can be neglected to simplify some analyses. More details are provided in \autoref{sec:results-discussions}.

\subsubsection{How the fluid flow profile is used}
\label{sec:how-fluid-flow}

@@

\noindent where \(g(t)\) is a dimensionless function that expresses the mathematical waveform of the pressure gradient, and  \(A\ped{t}\) is its amplitude,  adjusted in a convergence loop; the mass flow rate calculated from the Darcy velocity from \autoref{eq:75} is compared with the input value of mass flow rate until these values converge. The waveform $g(t)$ represents the fluid flow profile used.

@@

The canonical fluid flow profile considered in this work \textcolor{black}{ is the square wave or \emph{instantaneous profile}}, because of the instantaneous change in flow rate, as shown in \autoref{fig:mprofile}.

@@

The \textcolor{black}{instantaneous mass flow rate}, \(\rate{m}\ped{f}(t)\), is defined over a cycle with \textcolor{black}{a} period \(\tau\), and represents the fluid flow \textcolor{black}{through} a given regenerator bed. The so-called \emph{hot cycle}, \textcolor{black}{during which} the MCM is magnetized, occupies the \textcolor{black}{time interval} \(0 \le t < \nicefrac{\tau}{2}\), while the \emph{cold cycle}
lies \textcolor{black}{between} \(\nicefrac{\tau}{2} \le t \le \tau\). The flow profile oscillates between two plateaus of equal magnitude
\(\rate{m}\ped{f,max}\) \textcolor{black}{and} opposite directions, \textcolor{black}{which} are centered in each half-cycle. During the hot cycle, the cold
blow period is \(\tau\ped{CB}\), and during the cold cycle the hot blow period is \(\tau\ped{HB}\). If the flow is balanced, then \(\tau\ped{CB} = \tau\ped{HB}\).

During each half cycle, there are periods \textcolor{black}{without}  fluid flow, defined as:

@@

where HC and CC stand for hot \textcolor{black}{cycle} and cold cycle, respectively.

@@

When the blows have different time durations, the AMR cycle is considered unbalanced, and this \textcolor{black}{is known to have} a negative effect on performance \cite{bib:eriksen16_effec,bib:nakashima18-influen-exp}. In this work, the blows are always balanced, hence the blow fraction, the ratio of blow durations to cycle period \cite{bib:nakashima18-influen-exp}, can be evaluated as:

@@

\subsubsection{How the magnetic profile is used}
\label{sec:how-magnetic-profile}

The magnetic profile is modeled by a waveform of magnetic field strength $H(t)$ applied perpendicular to the regenerators, as shown in \autoref{fig:amrmodel}. The magnetic field is assumed uniform throughout the beds. The applied field is corrected from demagnetization effects to yield the effective field inside the regenerators:

@@

\noindent where the adiabatic temperature variation $\dtad$, a standard measure of the MCE, is calculated from \textcolor{black}{tabulated} experimental \textcolor{black}{data} for magnetocaloric materials as function of temperature and effective field. \cite{bib:trevizoli16_perfor_model}.

@@

The instantaneous profile (represented by the subscript ``IT'') and the rectified cosine profile (represented by ``RC'') are defined solely in terms of the \textcolor{black}{extreme} values $B\ped{min}$ and $B\ped{min}$, and are shown in \autoref{fig:itrc}.

@@

A suitable approximation of the instantaneous profile is the \textcolor{black}{\emph{magnetic ramp profile}, shown} in \autoref{fig:ramp}, with finite transition times between the levels of constant magnetization. The magnetic profile oscillates  between a low value \({B}\ped{min}\) and a high value \({B}\ped{max}\), and \textcolor{black}{remains} at each plateau for a period of \(\tau\ped{M}\). The plateaus are balanced and centered at each half-cycle.

@@

The \emph{ramp period} \(\tau\ped{R}\) \textcolor{black}{is} defined as:

@@

\nomenclature[azt]{$\tau\ped{R}$}{ramp period in the \textcolor{black}{magnetic} ramp profile [\si{\second}]}
\nomenclature[azt]{$\tau\ped{M}$}{magnetization period in the \textcolor{black}{magnetic} ramp  profile [\si{\second}]}
\nomenclature[azo]{$\theta\ped{R}$}{ramp rate in the \textcolor{black}{magnetic} ramp profile}

The magnetization fraction, \(F\ped{M}\), is the fraction of the cycle \textcolor{black}{during which} the magnetocaloric material is \textcolor{black}{subjected to a} constant magnetic field:

@@

Additionally, the average values of the magnetic field during each half-AMR cycle are considered for comparison between profiles. The average magnetic profile during the hot cycle ($0 \le t < \nicefrac{\tau}{2}$) is denoted $\average{B}\ped{high}$ and the average during the cold cycle  ($ \nicefrac{\tau}{2} \le t < \tau$) is denoted $\average{B}\ped{low}$. For the instantaneous waveform, these average values are identical to the extrema values.

@@

The fluid properties are considered constant in the momentum equation to decouple the solution \textcolor{black}{procedures to determine} the velocity and temperature fields. The properties are computed at the average temperature between the hot and cold sources temperatures, and are evaluated from interpolated tables exported from the EES software \cite{bib:klein13-ees}. In all simulations shown in this work, the heat transfer fluid is a mixture of water/ethylene-glycol with concentration \num{80}/\SI{20}{\percent} vol. For the energy equations, the fluid properties are also calculated from tabulated data, but the temperature dependence is considered.

In this work, both single- and multilayer regenerators are considered. Single-layer regenerators are composed of gadolinium,  a benchmark material with a Curie temperature of \SI{290}{\kelvin}. \textcolor{black}{For simplicity, the solid} density is assumed constant at $\rho\ped{s} = \SI{7900}{\kg\per\cubic\meter}$ and the solid \textcolor{black}{thermal} conductivity is set to $k\ped{s} = \SI{10.5}{\watt\per\meter\per\kelvin}$. The specific heat \textcolor{black}{capacity} of \ce{Gd} is calculated as a function of temperature and magnetic field based on experimental \textcolor{black}{data}, using a bi-linear interpolation scheme; more details on the experimental dataset \textcolor{black}{are available} in \cite{bib:trevizoli16_perfor_model}.

For the multilayer simulations, alloys of gadolinium and yttrium are used in the form \ce{Gd_{1-x}Y_x}, where $x$ is the yttrium fraction.  \textcolor{black}{This fraction} decreases the Curie temperature  \textcolor{black}{of the} alloy relative to that of pure gadolinium. Due to the lack of experimental  \textcolor{black}{data on the magnetocaloric properties of} \ce{Gd_{1-x}Y_x} alloys at the time \textcolor{black}{this analysis was made}, a simpler approach was used \textcolor{black}{in which} the properties of alloys with {a} low yttrium fraction are \textcolor{black}{identical to those} of pure gadolinium, except for the Curie temperature \textcolor{black}{(which is shifted to lower values)}.

@@

The AMR model considers only one bed and assumes $N\ped{r}$ identical beds experience the same cycle, multiplying the performance metrics below by this factor.

@@

The magnetic power to operate the AMR cycle is modeled as the ideal Carnot power, ignoring most thermal irreversibilities:

@@

\noindent while the fluid friction irreversibility is accounted for in the calculation of the pumping power:

@@

The hydraulic system to modulate the fluid flow through different regenerators at different time instants is composed of a pump and a set of electronic valves which can be precisely controlled to yield the desired blow durations. The electrical power consumed by the valve array is computed separately from other work contributions. An application of electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}.

Due to evolving developments in our group, two types of valves are considered, as will be elaborated in \autoref{sec:results-discussions}.

The first approach, called \emph{Type B valves}, uses the  model \textcolor{black}{of} \cite{bib:cardoso16_trans}, assuming that the individual consumption of each valve is independent of frequency and blow fraction. The valve power  $\wvalve$ can be computed as:

@@

Equation~\eqref{eq:198} was correlated for blow fractions of \num{50} and \SI{100}{\percent} and for frequencies in the range \textcolor{black}{of} \num{0.2}--\SI{1.6}{\hertz}, with an uncertainty \textcolor{black}{on} the order of \SI{0.4}{\watt} for a single valve. The use of different valve types will be discussed among the presented results.

Indepedent of the valve type used, it is also assumed that this valve system can produce the fluid flow profile \textcolor{black}{shown in} \autoref{fig:mprofile}, where the displaced fluid mass during one blow in one regenerator bed is $\rate{m}\ped{f,max} F\ped{B} \nicefrac{\tau}{2}$. The \emph{utilization factor} can then be calculated as:

@@

\nomenclature[bf]{$\Phi$}{utilization factor}
\noindent and in all results shown in this work, the number of valves is \textcolor{black}{calculated as}:

@@

The coefficient of performance \textcolor{black}{takes} the cooling capacity as \textcolor{black}{the main} output \textcolor{black}{parameter from} the AMR model, \textcolor{black}{in addition to} all previously cited power contributions:

@@

The analysis of magnetic profiles was performed in two different stages in the research of our group, as discussed below.

@@

In the first stage, the instantaneous and rectified cosine profiles are compared in the AMR model, considering monolayer regenerators without casing losses, and using Type B valves. The parameters used in all simulations are presented in \autoref{tab:params-cobem}.

\begin{table}[!ht]
  \centering
  \caption{AMR parameters kept fixed in the simulations with different magnetic profiles}
  \begin{tabular}{c|c}
\hline
\textbf{Parameter} & \textbf{Value}\\
\hline
   $D\ped{p}$ & \SI{0.5}{\mm}\\
$H\ped{r}$ & \SI{20}{\mm}\\
$W\ped{r}$ & \SI{25}{\mm}\\
$L\ped{r}$ & \SI{100}{\mm}\\
$N\ped{r}$ & 11 \\
$N\ped{v}$ & 22 \\
$T\ped{H}$ & \SI{298}{\kelvin}\\
$\tc$ & \SI{278}{\kelvin}\\
$\w\ped{NV}$ & \SI{4}{\watt}\\
$\w\ped{R}$ & \SI{0.36}{\watt}\\
\hline
  \end{tabular}

>>>>

\usepackage[numbers]{natbib}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{xcolor}
\usepackage{nomencl}
\usepackage{hyperref}

@@

\title{Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators
\thanks{
An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}).
}}

\author{
F\'{a}bio P. Fortkamp \and
Gusttav B. Lang \and
Jaime A. Lozano \and
Jader R. Barbosa Jr.
}

\institute{
F\'{a}bio P. Fortkamp \\
\email{fabio@polo.ufsc.br} \\
Gusttav B. Lang \and
Jaime A. Lozano \and
Jader R. Barbosa Jr.
\at
POLO --- Research Laboratories for Emerging Technologies in Cooling and Thermophysics, Department of Mechanical Engineering, Federal University of Santa Catarina, Florianópolis, SC, 88040-900, Brazil}

@@

\begin{abstract}
Magnetic cooling is an alternative to vapor compression that does not rely on the use of hazardous substances. The refrigerant is a solid material which reacts to oscillations in magnetic field by changing its temperature (the magnetocaloric effect). In active magnetic regenerators, the magnetocaloric material arranged as a porous medium is subjected to an oscillating fluid flow to allow heat transfer from a cold source to a hot sink in a thermodynamic cooling cycle. Although the  literature is abundant with studies on the influence of the fluid flow waveform on magnetic refrigeration devices, the influence of the magnetic field waveform has been much less investigated. In this work, we make use of an active magnetic regenerator numerical model with different mathematically-defined waveforms to determine which operating parameters yield the highest values of cooling capacity and coefficient of performance for a specific set of operating conditions. The results show that the best performance is achieved when the magnetic field is kept constant for the same time duration of the fluid flow through the magnetized material, and that the transition times between the high and low levels of the magnetic field should be as short as possible.

\keywords{magnetic refrigeration \and active magnetic regenerator \and numerical modeling \and magnetocaloric effect}
\end{abstract}

@@

Although mechanical vapor compression has been the dominant cooling technology for the past century \cite{bib:nik}, it still faces a number of challenges related to its environmental footprint. For instance, the phase-out of refrigerants with ozone depleting and global warming potentials brought about a more widespread use of flammable substances, which pose a new set of concerns, restrictions and new technological challenges for consumer applications \cite{bib:iir-flammable, bib:lionte18-adapt}.

Magnetic refrigeration (MR) is an emerging cooling technology which does not rely on hazardous fluids. In MR, the temperature of a  \emph{magnetocaloric material} (MCM) changes as a result of cyclical changes in the applied magnetic field due to the so-called \emph{magnetocaloric effect} (MCE). The magnitude of the MCE depends on  material properties, magnetic field variation and temperature, and it is maximum at the Curie temperature of the material \cite{bib:smith-magneto, bib:kitanovski}. Applications of the MCE at near room-temperature are not restricted to cooling applications; it can also be applied to the development of thermomagnetic motors \cite{bib:kaneko}.

@@

For operating temperatures typical of household cooling applications, the MCE is of the order of \num{2}-\SI{5} K/T. To amplify this temperature change, heat regeneration is usually employed \cite{bib:kitanovski}. Active magnetic regenerators (AMR) are thermal devices in which the magnetocaloric material is packed as a porous matrix subjected to periodic flow of an aqueous heat transfer fluid. The flow is put in sync with successive magnetization and demagnetization steps of the MCM in the porous bed to produce a refrigerating effect. Thus, the AMR is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously to build up a longitudinal temperature profile in the matrix. The layers can be made of the same material, resulting in a homogeneous regenerator. However, given the dependence of the MCE on temperature, it is desirable to build \emph{multilayer} regenerators, where each adjacent layer has a slightly different composition that will function around its own Curie temperature, maximizing the magnetocaloric effect of each portion.

@@

A typical AMR cycle is comprised of the following steps: (i) The magnetic circuit magnetizes the MCM, thereby increasing its temperature due to the MCE; (ii) During the \emph{cold blow}, cold fluid previously in thermal contact with the low-temperature source flows through the warm bed, absorbs its energy and releases it as heat to the high-temperature sink through the hot heat exchanger; (iii) The MCM is demagnetized and coold down as a result; (iv) As the fluid flow is reversed (\emph{hot blow}), it releases energy to the bed, decreases its temperature so it can absorb the thermal load at the cold heat exchanger in contact with the low-temperature source. Different cycles can be devised by changing the duration and synchronization  between the two cycle \emph{characteristic waveforms}:

\begin{enumerate}
\item The \emph{applied magnetic field profile}, which describes the oscillating magnetic field over one regenerator;
\item The \emph{fluid flow profile}, which describes the time-variation of flow rate through one bed.
\end{enumerate}

Fluid flow profiles can be more easily investigated  experimentally, as no changes in the fluid flow hardware are required. In particular, the effect of the \emph{duration} of the fluid blows has been extensively investigated \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}. There appears to be a consensus in the literature that the cooling capacity of magnetic refrigerators can be increased by displacing the fluid during periods where the magnetic field is at its extreme values.

In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied. Magnetic waveforms are usually investigated in terms of their synchronization with the fluid flow profile \cite{TUSEK20111507,bib:bjoerk11_amr}. \colorbox{yellow}{acho q cabe explicar brevemente o que os trabalhos de \cite{TUSEK20111507} e \cite{bib:bjoerk11_amr} fizeram...}. Trevizoli et al.~\cite{bib:trevizoli16_perfor_model} carried out a numerical comparison of the square wave (step change), sinusoidal and rectified cosine magnetic profiles. However, no systematic assessment of the effect of amplitude was performed nor did they investigate different geometries \colorbox{yellow}{nao estah claro o que vc quer dizer por geometries}.

\colorbox{yellow}{Fabio, acho que revisao bibliografica tem que ser expandida, trazendo trabalhos mais recentes em refrigeracao magnetica.}

\colorbox{yellow}{Tambem tem que trazer aqui para a revisao os nossos artigos que mediram/testaram/modelaram as valvulas.}

The present work bridges the gaps left in previous studies by investigating the performance of a magnetic refrigerator under different magnetic profile waveforms. These waveforms are mathematically modeled, and the cooling capacity and coefficient of performance are calculated based on the profiles parameters, while also investigated how the AMR geometry affect the performance in combinations with the magnetic profile. The fluid flow profile is assumed fixed in shape, although its parameters are also varied. To emulate constraints on an operating point of actual magnetic refrigeration devices, the temperature span is set fixed, and hence few comments are made on second-law efficiency.

@@

As previuosly explained, we performed numerical simulations using a previously developed AMR model, varying the profile-specific and geometric parameters. We also implemented a model to calculate the power consumption of a novel fluid management system, which is a topic not yet extensively studied in the literature. The output variables from this integrated model are the cooling capacity, the several power contributions (\colorbox{yellow}{specify}) and the coefficient of performance (COP).

@@

Simulations were performed using a one-dimensional AMR mathematical model, implemented using the Finite Volume Method \cite{bib:trevizoli16_perfor_model}. The model solves momentum and energy balance equations for the solid and fluid phases, represented by indices `s' and `f', respectively. The model geometry is shown in \autoref{fig:amrmodel}, and assumes that the regenerator is composed of monodisperse packed spheres with porosity $\varepsilon$.

@@

The momentum equation for the fluid domain is given by:

@@

\colorbox{yellow}{Fabio, talvez valha a pena explicar quem eh quem nos termos das equacoes da Q movimento e energias...}

Initial and boundary conditions, closure relations for the porous media terms, solution methods and convergence criteria and analyses are discussed in detail in \cite{bib:trevizoli16_perfor_model}. This AMR model solves the above equations for one regenerator operating between given sources temperatures (assuming ideal heat exchangers in contact with the thermal reservoirs), during one full cycle (hot and cold blows and  magnetization and demagnetization periods), given specified operating conditions (to be discussed later).

The casing heat transfer term $\rate{q}\ped{csg}$ in \autoref{eq:78} is calculated solving the heat conduction equation in the regenerator casing \cite{bib:trevizoli16_perfor_model}. It can be neglected in some circumstances if an insulating casing material is assumed, which greatly simplifies the analysis. %More details are provided in \autoref{sec:results-discussions}.

\subsubsection{Fluid flow profile modeling}
\label{sec:how-fluid-flow}

@@

\noindent where \(g(t)\) is a dimensionless function that expresses the mathematical waveform of the pressure gradient, and  \(A\ped{t}\) is its amplitude,  adjusted in a convergence loop. In this loop, the mass flow rate calculated in term of the Darcy velocity from \autoref{eq:75} is compared with the input   mass flow rate until convergence is obtained. %The waveform $g(t)$ represents the fluid flow profile used.

@@

The canonical fluid flow profile considered in this work is the square wave or \emph{instantaneous profile}, because of the instantaneous change in flow rate, as shown in \autoref{fig:mprofile}.

@@

The instantaneous mass flow rate, \(\rate{m}\ped{f}(t)\), is defined over a cycle with a period \(\tau\), and represents the fluid flow through a given regenerator bed. The so-called \emph{hot cycle}, during which the MCM is magnetized, occupies the time interval \(0 \le t < \nicefrac{\tau}{2}\), while the \emph{cold cycle} lies between \(\nicefrac{\tau}{2} \le t \le \tau\). The flow profile oscillates between two plateaus of equal magnitude
\(\rate{m}\ped{f,max}\) and opposite directions, which are centered in each half-cycle. During the hot cycle, the cold
blow period is \(\tau\ped{CB}\), and during the cold cycle the hot blow period is \(\tau\ped{HB}\). If balanced flow exists, then \(\tau\ped{CB} = \tau\ped{HB}\).

During each half cycle, there are periods without  fluid flow defined as:

@@

where HC and CC stand for hot cycle and cold cycle, respectively.

@@

When the blows have different time durations, the AMR cycle is considered unbalanced, and that is known to have a negative effect on performance \cite{bib:eriksen16_effec,bib:nakashima18-influen-exp}. In this work, the blows are always balanced, hence the blow fraction, i.e., the ratio of blow durations to cycle period \cite{bib:nakashima18-influen-exp}, can be evaluated as:

@@

\subsubsection{Magnetic profile modeling}
\label{sec:how-magnetic-profile}

The magnetic profile is modeled by a waveform of magnetic field strength, $H(t)$, applied perpendicular to the regenerators, as shown in \autoref{fig:amrmodel}. The magnetic field is assumed uniform throughout the beds. The applied field is corrected from demagnetization effects to yield the effective field inside the regenerators:

@@

\noindent where the adiabatic temperature variation, $\dtad$, a standard measure of the MCE, is calculated from tabulated experimental data for magnetocaloric materials as function of temperature and effective field. \cite{bib:trevizoli16_perfor_model}.

@@

The instantaneous (square wave) profile (represented by the subscript ``IT'') and the rectified cosine profile (represented by ``RC'') are defined solely in terms of the extreme values $B\ped{min}$ and $B\ped{min}$, and are shown in \autoref{fig:itrc}.

@@

A suitable approximation of the instantaneous profile is the \emph{magnetic ramp profile}, shown in \autoref{fig:ramp}, with finite transition times between the levels of constant magnetization. The magnetic profile oscillates  between a low value \({B}\ped{min}\) and a high value \({B}\ped{max}\), and remains at each plateau for a period of \(\tau\ped{M}\). The plateaus are balanced and centered at each half-cycle.

@@

The \emph{ramp period} \(\tau\ped{R}\) is defined as:

@@

\nomenclature[azt]{$\tau\ped{R}$}{ramp period in the magnetic ramp profile [\si{\second}]}
\nomenclature[azt]{$\tau\ped{M}$}{magnetization period in the magnetic ramp  profile [\si{\second}]}
\nomenclature[azo]{$\theta\ped{R}$}{ramp rate in the magnetic ramp profile}

The magnetization fraction, \(F\ped{M}\), is the fraction of the cycle during which the magnetocaloric material is subjected to a constant magnetic field:

@@

Additionally, the average values of the magnetic field during each half-AMR cycle are considered for comparison between profiles. The average magnetic profile during the hot cycle ($0 \le t < \nicefrac{\tau}{2}$) is denoted by $\average{B}\ped{high}$ and the average during the cold cycle  ($ \nicefrac{\tau}{2} \le t < \tau$) is denoted by $\average{B}\ped{low}$. For the instantaneous waveform, these average values are identical to the extreme values.

@@

The fluid properties are considered constant in the momentum equation to decouple the solution procedures to determine the velocity and temperature fields. The properties are computed at the average temperature between the hot and cold sources, and are evaluated from interpolation of tables imported from the EES software \cite{bib:klein13-ees}. In all simulations shown in this work, the heat transfer fluid is a \num{80}/\SI{20}{\percent} vol.~mixture of water/ethylene-glycol. For the energy equations, the fluid properties are also calculated from tabulated data, but the temperature dependence is considered.

Both single- and multilayer regenerators are considered in this study. Single-layer regenerators are composed of gadolinium,  a benchmark material with a Curie temperature of \SI{290}{\kelvin}. For simplicity, the solid density is assumed constant at $\rho\ped{s} = \SI{7900}{\kg\per\cubic\meter}$ and the solid thermal conductivity is set to $k\ped{s} = \SI{10.5}{\watt\per\meter\per\kelvin}$. The specific heat capacity of \ce{Gd} is calculated as a function of temperature and magnetic field based on experimental data, using a bi-linear interpolation scheme; more details on the experimental dataset are available in \cite{bib:trevizoli16_perfor_model}.

For the multilayer simulations, alloys of gadolinium and yttrium are used in the form \ce{Gd_{1-x}Y_x}, where $x$ is the yttrium fraction.  This fraction reduces the Curie temperature of the alloy relative to that of pure gadolinium. Due to the lack of experimental  data on the magnetocaloric properties of \ce{Gd_{1-x}Y_x} alloys at the time this analysis was made, a simpler approach was used in which the \textcolor{blue}{dependence of magnetization, specific heat capacity and entropy with respect to the magnetic field for} alloys with a low yttrium fraction are identical to those of pure gadolinium, \textcolor{blue}{but are shifted to a lower} Curie temperature (corresponding to the yttrium fraction).

\colorbox{yellow}{Fabio, veja se o texto acima estah ok...}

@@

The AMR model is solved for only one bed, but  assumes that the $N\ped{r}$ identical beds experience the same cycle. Thus, the extensive performance parameters are multiplied by that factor.

@@

\textcolor{blue}{As pointed out in \colorbox{yellow}{citar o paper da ATE - Design trade-offs}, since external sources of irreversibility (e.g., heat transfer with a finite temperature difference in the heat exchangers) are ignored and no eddy currents and hysteresis losses are present,} the magnetic power required to \textcolor{blue}{magnetize the solid refrigerant and produce the MCE} in the AMR cycle is given by the product of the Carnot efficiency and the cooling capacity as follows:

@@

Irreversibility due to fluid friction is accounted for in the calculation of the pumping power:

@@

The hydraulic system designed to modulate the fluid flow through different regenerators at different time instants is composed of a pump and a set of electronic valves which can be precisely controlled to yield the desired blow durations. The electrical power consumed by the valve array is computed separately from other work contributions. An application of electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}.

\colorbox{yellow}{Fabio, a ultima frase do paragrafo acima nao  cabe aqui... quero dizer que a aplicacao deveria ter sido discutida na revisao bibliografica, a qual precisa ser expandida}

%Due to evolving developments in our group, two types of valves are considered, as will be elaborated in \autoref{sec:results-discussions}.

In the present analysis, two types of valves are considered. In the first approach, called \emph{Type B valves}, the  model proposed in Ref.~\cite{bib:cardoso16_trans} is used, assuming that the individual consumption of each valve is independent of frequency and blow fraction. The valve power  $\wvalve$ can be computed as:

\colorbox{yellow}{da mesma forma, o trabalho \cite{bib:cardoso16_trans} tem que constar da revisao bibliografica...}

\colorbox{yellow}{fica estranho o \textbf{primeiro} approach ser Type B e o \textbf{segundo} ser Type A...}

@@

\colorbox{yellow}{A equacao acima precisa ser melhor contextualizada. Talvez os revisores pecam para dar uma descricao minima do experimento. Uma saida para nao ter que fazer isso seria revisar na introducao o trabalho nosso que mediu e propos a correlacao (foi o do Pedroca)  }

Equation~\eqref{eq:198} was correlated for blow fractions of \num{50} and \SI{100}{\percent} and frequencies in the range of \num{0.2}--\SI{1.6}{\hertz}, with an uncertainty on the order of \SI{0.4}{\watt} for a single valve. The use of different valve types will be discussed among the presented results.

Independent of the valve type used, it is also assumed that each valve system can produce the fluid flow profile shown in \autoref{fig:mprofile}, where the displaced fluid mass during one blow in one regenerator bed is $\rate{m}\ped{f,max} F\ped{B} \nicefrac{\tau}{2}$. The \emph{utilization factor} can then be calculated as:

@@

\nomenclature[bf]{$\Phi$}{utilization factor}
\noindent and in all results shown in this work, the number of valves is calculated as:

@@

The coefficient of performance takes the cooling capacity as the main output parameter from the AMR model, in addition to all previously cited power contributions:

@@

The analysis of magnetic profiles was performed at two different stages. Initially, the instantaneous (square-wave) and the rectified cosine profiles are compared using a simpler approach (i.e., neglecting casing losses). Later, based on the selection of the most promising magnetic profile, a more in-depth analysis is carried out to determine the optimal geometric and operating parameters of the AMR system.

@@

At the first stage of the present analysis, the instantaneous and rectified cosine profiles are compared considering a single-layer regenerator  without casing losses, using Type B valves. The parameters used in all simulations are presented in \autoref{tab:params-cobem}.

\begin{table}[!ht]
  \centering
  \caption{AMR parameters kept fixed in the simulations with different magnetic profiles \colorbox{yellow}{Fabio, acho que as variaveis nao foram apresentadas na lista de simbolos}}
  \begin{tabular}{c|c}
\hline
\textbf{Parameter} & \textbf{Value}\\
\hline
   $D\ped{p}$ & \SI{0.5}{\mm}\\
$H\ped{r}$ & \SI{20}{\mm}\\
$W\ped{r}$ & \SI{25}{\mm}\\
$L\ped{r}$ & \SI{100}{\mm}\\
$N\ped{r}$ & 11 \\
$N\ped{v}$ & 22 \\
$T\ped{H}$ & \SI{298}{\kelvin}\\
$\tc$ & \SI{278}{\kelvin}\\
$\w\ped{NV}$ & \SI{4}{\watt}\\
$\w\ped{R}$ & \SI{0.36}{\watt}\\
\hline
  \end{tabular}
